Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-07-02 review_article.Rmd
USA melanoma plots, coloured by rate, sized by population

---
title: "Cartogram Mapping and its Application to Cancer Data Visualisation"
author: "Stephanie Kobakian, Jessie Roberts and Dianne Cook"
bibliography: reviewbib.bib
output:
  html_document: default
fontsize: 11pt
link-citations: yes
number_sections: no
fig_caption: yes
biblio-style: vancouver
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<!--
Author notes:
6000 words maximum.
focused  application  of  literature  to address  a  relevant  clinical  issue:
Mapping cancer outcomes
Cartogram applications should point to examples of cancer outcomes, with the main cartogram section discussing sources considered in grey literature review. Examples of political areas may be considered if cancer data is aggregated at these levels.

Future steps should consider applications not currently utilised for cancer outcome displays, where their use may improve decision making
-->

@@

## Disease mapping

>>>>

---
title: "Cartogram Mapping and its Application to Cancer Data Visualisation"
author: "Stephanie Kobakian, Jessie Roberts and Dianne Cook"
bibliography: reviewbib.bib
output:
  html_document: default
fontsize: 11pt
link-citations: yes
number_sections: yes
fig_caption: yes
biblio-style: vancouver
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<!--

Please note that the submission deadline is September 30, 2019.

Author notes:
6000 words maximum.
focused  application  of  literature  to address  a  relevant  clinical  issue:
Mapping cancer outcomes
Cartogram applications should point to examples of cancer outcomes, with the main cartogram section discussing sources considered in grey literature review. Examples of political areas may be considered if cancer data is aggregated at these levels.

- Future steps should consider applications not currently utilised for cancer outcome displays, where their use may improve decision making
- needs to have a clear relevance to spatial patterns in cancer epidemiology
- presents alternative ways of visualising those spatial patterns, or the uncertainty in those patterns
- a more applied-focussed paper (eg lots of cool images), rather than theoretical (eg lots of formula).
-->

@@

## Introduction
<!--
Current best practices: Choropleths
Current exploratory practices: Cartograms: cont, non cont, (tilegrams, dorlings)
Suggested uses of 
-->

## Disease mapping methods
